Results

### 2025-10-06 notebooks/00_index.qmd
feat: finalize paper figures

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using Discontinuity: compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using SPEDAS
using DimensionalData
using DataFrames, DataFramesMeta
using SpacePhysicsMakie, GLMakie
using SPEDAS: setmeta, setmeta!
using Beforerr: _theme_legend, easy_save
using PartialFunctions

@@

```{julia}
df = workload()
compute_params!(df)
compute_Alfvenicity_params!(df)

@@

```{julia}
compute_PSP_anisotropy_params!(psp_df)
for enc in 7:9
    tmin_wind, tmax_wind = get_timerange(enc)[2]
    wind_df_enc = @rsubset(wind_df, :enc == enc; view=true)
    compute_Wind_anisotropy_params!(wind_df_enc, tmin_wind, tmax_wind)

@@

```{julia}
f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[5, :]
fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_conf, Second(10))
@info "v_l_ratio" psp_event.V_l_ratio psp_event.V_l_ratio_max
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_conf)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_conf)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_conf)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_conf, Second(10))
f
```

@@

## Thickness, current density comparison and Alfvénicity

```{julia}
using AlgebraOfGraphics
using Discontinuity: compute_params!, compute_Alfvenicity_params!
using Beforerr
using Beforerr: add_labels!
# using CairoMakie
using StatsBase
# CairoMakie.activate!()

set_AoG_theme!()
formats = (:pdf,)

# df, configs = workload()
compute_params!(df)

# AoG fix
using LaTeXStrings
import AlgebraOfGraphics: append_unit_string
append_unit_string(s::LaTeXStrings.LaTeXString, u::String) = s
```

```{julia}
fname = "properties_xy_comp-enc"

for enc in 7:9, 𝐧 in [:mva, :cross]
    view = true
    𝒎 = var_mapping(; 𝐧)

    tdf = subset_𝐧(dropmissing(@subset(df, :enc .== enc; view)), 𝐧)
    compute_Alfvenicity_params!(tdf)
    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=8, legend=(; alpha=1)) * mapping(color=:id, marker=:id)

    fig = Figure(size=(800, 300))
    axis = (; yscale=log10, xscale=log10)
    v_axis = (; yscale=log10, xscale=log10, limits=((2, 400), (2, 400)))

    ga = fig[1, 1]
    gb = fig[1, 2]
    gc = fig[1, 3]

    spec1 = plt * mapping(𝒎.l, 𝒎.j)
    spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
    spec3 = plt * mapping(𝒎.v_Alfven, 𝒎.v_ion)

    grid1 = draw!(ga, spec1; axis)
    draw!(gb, spec2; axis)
    draw!(gc, spec3; axis=v_axis)

    slopes = (1.0, 0.7, 0.4, 0.1)
    foreach(slopes) do s
        lines!(1 .. 1000, (*)$s, linestyle=:dash, label="$s")
    end
    axislegend("slope", position=:lt)

    pretty_legend!(fig, grid1)
    add_labels!([ga, gb, gc])
    easy_save("$fname-$enc-$𝐧"; formats, force=true)
    display(fig)
end
```

![](../figures/properties_xy_comp-enc-7-mva.pdf)
![](../figures/properties_xy_comp-enc-7-cross.pdf)
![](../figures/properties_xy_comp-enc-8-mva.pdf)
![](../figures/properties_xy_comp-enc-8-cross.pdf)
![](../figures/properties_xy_comp-enc-9-mva.pdf)
![](../figures/properties_xy_comp-enc-9-cross.pdf)

```{julia}
for enc in 7:9
    tdf = filter_low_mva_quality(dropmissing(@subset(df, :enc .== enc; view=true), view=true))
    data_layer = data(tdf)
    legend = (; markersize=10, alpha=1)
    plt = data_layer * visual(Scatter; markersize=4, alpha=0.618, legend) * mapping(color=:id, marker=:id)

    fig = Figure(size=(800, 400))
    axis = (; yscale=identity, xscale=identity)

    ga = fig[1, 1]
    gb = fig[1, 2]

    spec1 = plt * mapping(𝒎.bn, 𝒎.ω)
    spec2 = plt * mapping(𝒎.bn, 𝒎.ω_in)

    grid1 = draw!(ga, spec1; axis)
    draw!(gb, spec2; axis)

    pretty_legend!(fig, grid1)
    add_labels!([ga, gb])
    display(fig)
end
```

>>>>

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using Discontinuity: compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using SPEDAS
using DimensionalData
using DataFrames, DataFramesMeta
using SpacePhysicsMakie, GLMakie
using SPEDAS: setmeta, setmeta!
using Beforerr: _theme_legend, easy_save, hideylabel!
using PartialFunctions

@@

```{julia}
df = workload()

@@

```{julia}
compute_params!(df)
compute_Alfvenicity_params!(df)

compute_PSP_anisotropy_params!(psp_df)
for enc in 7:9
    tmin_wind, tmax_wind = get_timerange(enc)[2]
    wind_df_enc = @rsubset(wind_df, :enc == enc; view=true)
    compute_Wind_anisotropy_params!(wind_df_enc, tmin_wind, tmax_wind)

@@

```{julia}
let add_fit = true, add_Va = true
    f = Figure(; size=(450, 400))
    faxs, = plot_candidate(f[1, 1], filter_low_mva_quality(psp_df)[20, :], psp_conf, Second(4); add_fit, legend=nothing, add_Va)
    faxs, = plot_candidate(f[1, 2], filter_low_mva_quality(thm_df)[12, :], thm_conf, Second(2); add_fit, add_Va)
    hideylabel!.(faxs.axes)
    add_labels!(f[1, 1]; position=Left(), padding=(30, -30, 0, 0), labels=1:3, open="(a.")
    add_labels!(f[1, 2]; position=Left(), padding=(30, -30, 0, 0), labels=1:3, open="(b.")
    # faxs, = plot_candidate(f[1, 3], filter_low_mva_quality(wind_df)[2, :], wind_conf, Second(6); add_fit)
    # hideylabel!.(faxs.axes)
    colgap!(f.layout, 1)
    resize_to_layout!(f)
    easy_save("event-example")
    f
end
```

```txt
  :t_us              => 2021-01-15T04:05:04.549
  :t_ds              => 2021-01-15T04:05:17.957
  :tstart            => 2021-01-15T04:05:04
```

@@
